---
title: How to Make Awesome R Markdown for Blogdown
author: John Houghton
date: '2018-11-13'
slug: how-to-make-awesome-r-markdown-for-blogdown
categories:
  - Markdown
  - R
tags: []
description: ''
featured: ''
featuredalt: ''
featuredpath: ''
linktitle: ''
output:
  html_document:
    code_folding: hide
    df_print: knitr::kable
    toc: true
    toc_float: true 
---
output:rmdformats::html_clean: 
    toc: yes
    toc_depth: 2
self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: kate
```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
# options(max.print="75")
# opts_chunk$set(echo=TRUE,
# 	             cache=FALSE,
#                prompt=FALSE,
#                tidy=TRUE,
#                comment=NA,
#                message=FALSE,
#                warning=FALSE)
# # opts_knit$set(width=75)
```

```{r cache=FALSE}
knitr::read_chunk('~/Documents/Github/r_snippets/blogdown.R')
```
# R Notebook Options
```{r knitr_optionss, include=TRUE}
```

# Tabbed Section
## title {.tabset .tabset-fade}
content above tabbed region.

### tab 1 

tab content 1

### tab 2

tab content 2

##

content below tabbed region

## Quarterly Results {.tabset .tabset-fade .tabset-pills}
### By Product
```{r}
data(iris)
iris
```
### By Region
```{r}
iris
```
#### sdf

# Reference 
## blogdown documentation here: https://bookdown.org/yihui/rmarkdown/html-document.html
## Knitr Examples on Github
https://github.com/yihui/knitr-examples
## CheatSheet 
https://www.ethz.ch/content/dam/ethz/special-interest/math/statistics/sfs/Education/Advanced%20Studies%20in%20Applied%20Statistics/course-material-1719/Datenanalyse/rmarkdown-2.pdf

# Markdown Themes
### rmdformats package  https://github.com/juba/rmdformats
The github README.md provides some good examples

Here's a great collection of examples of themes
http://www.datadreaming.org/post/r-markdown-theme-gallery/



## Quarterly Results {.tabset}

### By Product

(tab content)

### By Region

(tab content)

