---
title: A Markdown Test
author: John Houghton
date: '2018-11-12'
slug: a-markdown-test
categories:
  - R
tags: []
description: ''
---


# Resources
#### Performance Analysis Vignette
https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ05-performance-analysis-with-tidyquant.html

#### Really great article I walked through
https://rstudio-pubs-static.s3.amazonaws.com/333431_8a130f2ff7f84e4faee2a4ac01d6c30e.html

#### Really great article #2 - same as above or extended?
https://rpubs.com/mr148/333431

####Backtesting 4 Portfolio Optimization Strategies In R
https://seekingalpha.com/article/4166115-backtesting-4-portfolio-optimization-strategies-r

##### Using ROI Solvers for Portfolio Analytics, Vignette
https://rdrr.io/cran/PortfolioAnalytics/f/inst/doc/ROI_vignette.pdf

# R Notebook Options
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, progress = TRUE, verbose = TRUE, error=TRUE, cache = TRUE)
```

# Load Required Libraries & Set Paths
```{r}
library(tidyverse)
library(tidyquant)
library(lubridate)
library(timetk)
setwd("~/Documents/GitHub/rob_gordon_2018")
```

# Set Query Parameters
```{r, echo=FALSE, warning=FALSE}
from_date <- Sys.Date() - years(5) # months(6)
to_date <- Sys.Date()
```

# Get Stock Data
```{r, echo=FALSE, warning=FALSE}
stocks <- c("SPY", "IYR", "QQQ", "TLT", "GLD", "IWM", "EEM", "DBC", "EFA")

stock_data <- tq_get(stocks
                     , get  = "stock.prices"
                     , from = from_date
                     , to = to_date) 
stock_data %>% head(100)
```

# Visualize Stock Prices 
```{r}
# using quantmod
library(quantmod)
getSymbols("SPY")
chartSeries(SPY)
chartSeries(SPY, subset='last 6 months') # ,theme=chartTheme('white'), TA=NULL
addMACD()   #  add MACD indicator to current chart

# using ggplot2
stock_data %>%
    filter(symbol %in% c("SPY", "GLD", "QQQ", "DBC")) %>%
    ggplot(aes(x = date, y = adjusted, color = symbol)) +
    geom_line(size = 1) +
    labs(title = "Daily Stock Prices",
         x = "", y = "Adjusted Prices", color = "") +
    facet_wrap(~ symbol, ncol = 2, scales = "free") +
    scale_y_continuous(labels = scales::dollar) +
    theme_tq() + 
    scale_color_tq()

library(ggthemes) 
stock_data %>%
  filter(symbol %in% c("SPY", "GLD", "QQQ", "DBC")) %>%
  ggplot(aes(x = date, y = adjusted)) +
geom_line() + # Plot stock price
geom_bbands(aes(high = high, low = low, close = close), ma_fun = SMA, n = 100,show.legend=TRUE) +
ggthemes::theme_hc() +
  scale_colour_hc()+facet_wrap(~  symbol, ncol = 2,scales = "free") 
```


```{r}
#######################################################
### !!! THIS DOES NOT ALIGN WITH ANYTHING ELSE !!!! ###
#######################################################

library(quantmod)
getSymbols('SPY',src='yahoo')
# allReturns(SPY)  # returns all periods

simple_return <- periodReturn(SPY,period='yearly',subset='2012::') 
simple_return %>% plot(type = "l", col = "blue", lwd = 2, ylab = "Dollars", main = "Arithmetic FV of $1 @ sbux")
simple_return %>% as.tibble() %>% mutate(type='arithmetic', date = row.names(.))

log_return <- periodReturn(SPY,period='yearly',subset='2012::', type='log') 
log_return %>% as.tibble() %>% mutate(type="log", date = row.names(.))
log_return %>% plot(type = "l", col = "blue", lwd = 2, ylab = "Dollars", main = "Log FV of $1 @ sbux")
```

# Calculate Returns
```{r, echo=FALSE, warning=FALSE}
# simple returns = Rt = [ Pt - Pt-1 ]/ Pt-1
simple_returns <- 
  stock_data %>% 
  group_by(symbol, year = year(date)) %>%
  summarise(adjusted = last(adjusted, order_by = year)) %>% 
  mutate(return = (adjusted - lag(adjusted, order_by = year)) / lag(adjusted, order_by = year)
         , return = round(return, 6)) %>% 
  arrange(desc(symbol), desc(year)) 
  # %>% filter(symbol == "SPY")
simple_returns  

# continuously compounded returns = rt=ln(1+Rt)  

# tidyquant returns -- same as simple calced returns, above.
mo_returns <- stock_data %>% 
  group_by(symbol) %>%
  tq_transmute(select = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "returns") %>% 
  mutate(returns = round(returns, 6)) %>% 
  arrange(desc(symbol), desc(date)) 
  # %>% filter(symbol == "SPY")
mo_returns 

# chart returns
mo_returns %>% 
  filter(symbol %in% c("SPY", "GLD", "QQQ", "DBC")) %>%
    ggplot(aes(x = date, y = returns, fill = symbol)) +
    geom_line(aes(color=symbol)) +
    geom_hline(yintercept = 0, color = palette_light()[[1]]) +
    scale_y_continuous(labels = scales::percent) +
    labs(title = " Monthly Returns",
         subtitle = "",
         y = "Monthly Returns", x = "") + 
    facet_wrap(~ symbol, ncol = 2,scales = "free") +
    theme_tq() + 
    scale_fill_tq()

# Chart Smoothed Returns
mo_returns %>% 
  filter(symbol %in% c("SPY", "GLD", "QQQ", "DBC")) %>%
    ggplot(aes(x = date, y = returns, fill = symbol)) +
    geom_smooth(aes(color=symbol),method = 'loess' , formula = y ~ x) +
    geom_hline(yintercept = 0, color = palette_light()[[1]]) +
    scale_y_continuous(labels = scales::percent) +
    labs(title = " Monthly Returns",
         subtitle = "",
         y = "Monthly Returns", x = "") + 
    facet_wrap(~ symbol, ncol = 2,scales = "free") +
    theme_tq() + 
    scale_fill_tq()

```

# Growth of $1000 version 1
```{r}
init.investment <- 1000
mo_returns %>% arrange(date) %>%
    mutate(wealth.index = init.investment * cumprod(1 + returns)) %>%
    ggplot(aes(x = date, y = wealth.index, color = symbol)) +
    geom_line(size = 2, color = palette_light()[[3]]) +
    geom_smooth(method = "loess") +
    labs(title = "Individual Portfolio: Comparing the Growth of $1K",
         subtitle = "Quickly visualize performance",
         x = "", y = "Investment Value") +
    theme_tq() +
    scale_y_continuous(labels = scales::dollar)
```

# Growth of $1000 version 2
```{r}
# example = chart.CumReturns {PerformanceAnalytics}
periodReturn(SPY, period='yearly',subset='2012::', type='arithmetic', leading=FALSE) %>% 
  chart.CumReturns()

chart.CumReturns(stock_returns, wealth.index = TRUE, main="Growth of $1") 
```


# Create Time-Series Object for Optimization
```{r}
# convert to ts object
stock_returns <- mo_returns %>% 
  # filter(symbol %in% c("SPY", "GLD", "QQQ", "DBC")) %>%
  spread(key = symbol, value = returns) %>%
  tk_xts(date_var = date) %>% 
  na.omit()
```

# Portfolio Optimization
```{r}
# Markowitz Optimization involves minimizing the risk(variance) of returns and maximizing returns.
# https://rstudio-pubs-static.s3.amazonaws.com/333431_8a130f2ff7f84e4faee2a4ac01d6c30e.html
library(PortfolioAnalytics)

# Loading all suggested packages to fix ROI issue
list.of.packages <- c("foreach", "DEoptim", "iterators", "fGarch", "Rglpk", "quadprog", "ROI", "ROI.plugin.glpk", "ROI.plugin.quadprog", "ROI.plugin.symphony", "pso", "GenSA", "corpcor", "testthat", "nloptr", "MASS", "robustbase")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

# Create portfolio object
portf_minvar <- portfolio.spec(assets = colnames(returns.portfolio))
# Add full investment constraint to the portfolio object
portf_minvar <- add.constraint(portfolio=portf_minvar, type="full_investment")
# Add objective to minimize variance
portf_minvar <- add.objective(portfolio=portf_minvar, type="risk", name="var")
# Add long only constraints
portf_minvar <- add.constraint(portfolio=portf_minvar, type="box", min=0, max=1)
 # Run the optimization
opt_gmv <- optimize.portfolio(R=returns, portfolio=portf_minvar, optimize_method="ROI", trace=TRUE)
print(opt_gmv)
#summary(opt_gmv)
```

# Visualize Portfolio Optimization
```{r, echo=FALSE, warning=FALSE}
wts <- c(0.0707, 0.3400, 0.0000, 0.5893)
principal <- 10000
portfolio_growth_monthly <- mo_returns %>%
  filter(symbol %in% c("DBC", "GLD", "QQQ", "SPY")) %>% 
    tq_portfolio(assets_col   = symbol, 
                 returns_col  = returns, 
                 weights      = wts, 
                 col_rename   = "investment.growth",
                 wealth.index = TRUE) %>%
    mutate(investment.growth = investment.growth * principal)
portfolio_growth_monthly %>%
    ggplot(aes(x = date, y = investment.growth)) +
    geom_line(size = 2, color = palette_light()[[1]]) +
    labs(title = "Optimized Portfolio Growth",
         subtitle = "",
         caption = "Now we can really visualize performance!",
         x = "", y = "Portfolio Value") +
    geom_smooth(method = "loess") +
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar)

opt_gmv %>% chart.RiskReward()
# opt_gmv %>% chart.EfficientFrontier(n.portfolios = 1)
opt_gmv %>% chart.Weights()
# opt_gmv %>% chart.RiskBudget()
```

####################
### TRY R CHARTS ###
####################

####################
### TRY SLIDFY ###
####################

### BACKTESTING PORTFOLIOS ###
```{r}
# https://rdrr.io/cran/PortfolioAnalytics/f/inst/doc/ROI_vignette.pdf
bt_gmv <- optimize.portfolio.rebalancing(R=returns, portfolio=portf_minvar,
                                         optimize_method="ROI",
                                         rebalance_on="quarters",
                                         training_period=36)
bt_gmv
```

# Get Performance ### 
```{r}
# descriptive statistics
mo_returns %>% tq_performance(Ra = returns, Rb = NULL, performance_fun = table.Stats)
# annualized returns
mo_returns %>% tq_performance(Ra = returns, Rb = NULL, performance_fun = table.AnnualizedReturns)
# correlations - REQUIRES BASELINE
###mo_returns %>% tq_performance(Ra = returns, Rb = Rb, performance_fun = table.Correlation)
# downside risks
mo_returns %>% tq_performance(Ra = returns, Rb = NULL, performance_fun = table.DownsideRisk)
# downside risk ratios
mo_returns %>% tq_performance(Ra = returns, Rb = NULL, performance_fun = table.DownsideRiskRatio)
# value at risk
mo_returns %>% tq_performance(Ra = returns, Rb = NULL, performance_fun = VaR)
# sharpe ratio
mo_returns %>% tq_performance(Ra = returns, Rb = NULL, performance_fun = SharpeRatio)
```

# Example of Efficiency Frontier from Stack Overflow
https://stackoverflow.com/questions/30614457/r-portfolio-analytics-chart-efficientfrontier-function/30650972#30650972
```{r}
library(PortfolioAnalytics)
  returns <- stock_returns
#  define moment function
  annualized.moments <- function(R, scale=12, portfolio=NULL){
    out <- list()
    out$mu <-    matrix(colMeans(R), ncol=1)
    out$sigma <- cov(R)/scale
    return(out)
  }
# define portfolio
  prt <- portfolio.spec(assets=colnames(returns))
  prt <- add.constraint(portfolio=prt, type="long_only")
  #  leverage defaults to weight_sum = 1 so is equivalent to full_investment constraint
  prt <- add.constraint(portfolio=prt, type="leverage")
  prt <- add.objective(portfolio=prt, type="risk", name="StdDev")
# calculate and plot efficient frontier
  prt_ef <- create.EfficientFrontier(R=12*returns, portfolio=prt, type="mean-StdDev", 
                                      match.col = "StdDev", momentFUN="annualized.moments", scale=12)
  xlim <- range(prt_ef$frontier[,2])*c(1, 1.5)
  ylim <- range(prt_ef$frontier[,1])*c(.80, 1.05)
  chart.EfficientFrontier(prt_ef, match.col="StdDev", chart.assets = FALSE, 
                          labels.assets = FALSE, xlim=xlim, ylim=ylim )
  points(with(annualized.moments(12*returns, scale=12), cbind(sqrt(diag(sigma)), mu)), pch=19 ) 
  text(with(annualized.moments(12*returns, scale=12), cbind(sqrt(diag(sigma)), mu)), 
       labels=colnames(returns), cex=.8, pos=4) 
  chart.EF.Weights(prt_ef, match.col="StdDev")
  chart.EfficientFrontier(prt_ef)
```
# Second Example from Stack Overflow
https://stackoverflow.com/questions/30614457/r-portfolio-analytics-chart-efficientfrontier-function/30650972#30650972
```{r}
require(quadprog) 
#min_x(-d^T x + 1/2 b^T D x) r.t A.x>=b
MV_QP<-function(nx, tarRet, Sig=NULL,long_only=FALSE){
  if (is.null(Sig)) Sig=cov(nx)
  dvec=rep(0,ncol(Sig))
  meq=2
  Amat=rbind(rep(1,ncol(Sig)),
             apply(nx,2,mean) )
  bvec=c(1,tarRet )
  if (long_only) {
    meq=1
    Amat=Amat[-1,]
    Amat=rbind(Amat,
               diag(1,ncol(Sig)),
               rep(1,ncol(Sig)),
               rep(-1,ncol(Sig)))
    bvec=bvec[-1]
    bvec=c(bvec,
               rep(0,ncol(Sig)),.98,-1.02)
  }
  sol  <- solve.QP(Dmat=Sig, dvec, t(Amat), bvec, meq=meq)$solution 
}

steps=50
x=returns
 µ.b <- apply(X = x, 2, FUN = mean) 
long_only=TRUE
range.bl <- seq(from = min(µ.b), to = max(µ.b)*ifelse(long_only,1,1.6), length.out = steps) 
risk.bl <- t(sapply(range.bl, function(targetReturn) { 
  w <- MV_QP(x, targetReturn,long_only=long_only) 
  c(sd(x %*% w),w)  }))

weigthsl=round(risk.bl[,-1],4)
colnames(weigthsl)=colnames(x)
weigthsl %>% head()
risk.bl=risk.bl[,1]
rets.bl= weigthsl%*%µ.b
fan=12
plot(x = risk.bl*fan^.5, y = rets.bl*fan,col=2,pch=21,
     xlab = "Annualized Risk ", 
     ylab = "Annualized Return", main = "long only EF with solve.QP")
```

# Calculate Returns, Method 2
https://ntguardian.wordpress.com/2017/03/27/introduction-stock-market-data-r-1/
(Here, \log is the natural log, and our definition does not depend as strongly on whether we use \log(\text{price}_{t}) - \log(\text{price}_{t - 1}) or \log(\text{price}_{t+1}) - \log(\text{price}_{t}).) The advantage of using log differences is that this difference can be interpreted as the percentage change in a stock but does not depend on the denominator of a fraction.


# Example - Multi Layer Optimization
```{r}
demo(multi_layer_optimization)
```

# Awesome Interactive Example!!!!!
```{r}
#get the data and convert to a format that we would expect from melted xts
#will be typical
#also original only uses a single value (val) and not other 
require(reshape2)
require(PerformanceAnalytics)
data(managers)
managers <- na.omit(managers)
managers.melt <- melt(
  data.frame( index( managers ), coredata(cumprod( managers+1 )*100 ) ),
  id.vars = 1
)
colnames(managers.melt) <- c("date", "manager","val")
managers.melt[,"date"] <- format(managers.melt[,"date"],format = "%Y-%m-%d")

require(devtools)
install_github('ramnathv/rCharts')
require(rCharts)
p2 <- rCharts$new()
p2$setLib('libraries/widgets/nyt_home')
p2$setTemplate(script = "libraries/widgets/nyt_home/layouts/nyt_home.html")
p2$set(
  description = "This data comes from the managers dataset included in the R package PerformanceAnalytics.",
  data = managers.melt,
  groups = "manager"
)
cat(noquote(p2$html()))


```

# Backtesting 4 Portfolio Optimization Strategies In R
https://seekingalpha.com/article/4166115-backtesting-4-portfolio-optimization-strategies-r

